Untitled

### 2025-04-06 script/r/draft.Rmd
maj gitignore

>>>>

```{r}
df <- readRDS("data/data_rds/data_final.rds")

df %<>%
  filter(spl==1, round==5)

radius<- 5000

df_sf_buff <- df[, .(longitude, latitude, iso, id_ea)] %>%
  vect(geom = c("longitude", "latitude"), crs = "EPSG:4326") %>%
  buffer(width = radius)

if (any(!is.valid(df_sf_buff))) {
  df_sf_buff <- make_valid(df_sf_buff)
}

cty_shp <- vect("data/data_raw/gadm/gadm41_BEN_2.shp")

cty_buff <- intersect(df_sf_buff, cty_shp)

cty_sf <- st_as_sf(cty_shp)
cty_buff_sf <- st_as_sf(cty_buff)

ggplot() +
  geom_sf(
    data = cty_sf,
    fill = "lightgray",
    color = "black",
    alpha = 0.5
  ) +

  geom_sf(
    data = cty_buff_sf,
    fill = "gold",
    color = "gold4",
    alpha = 0.3
  ) +

  theme_minimal() +
  labs(title = "Circles 10km radius")

```{r}
rc <- function(x) {
  ifelse(is.na(x), 0 , 1)
}

# Define TIFF file path
tiff_file <- "data/data_raw/collins_recode/Mobile Coverage Explorer v2012 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_BEN2G_2012.tif"

# Filter circles based on ISO code
circles <- df_sf_buff[df_sf_buff$iso == "BEN"]

# Harmonize CRS to WGS84 using terra::project()
target_crs <- "EPSG:4326"  # WGS84 CRS

# Load and process raster using terra (faster than raster)
gg <- rast(tiff_file)
plot(gg)
gg_wgs84 <- project(gg, target_crs)
plot(gg_wgs84)
gg_wgs84_recode <- app(gg_wgs84, fun = rc)
plot(gg_wgs84_recode)

# Check the extent of circles to ensure it's valid
circles_extent <- ext(circles)

plot(circles)
plot(circles_extent)
# Crop and mask raster to the buffered areas
gg_wgs84_cropped <- crop(gg_wgs84_recode, circles_extent)
gg_wgs84_masked <- mask(gg_wgs84_cropped, circles)
plot(gg_wgs84_cropped)
plot(gg_wgs84_masked)

global(gg_wgs84_masked, mean, na.rm = TRUE)

circles_cropped <- crop(circles, gg_wgs84_masked)

plot(circles_cropped, add = TRUE, border = "red")

# Extract values from the raster based on the polygons
gg_values <- terra::extract(gg_wgs84_masked,
                            circles_cropped,
                            fun = mean,
                            na.rm = TRUE)

circles_cropped$gg_mean <- gg_values[, 2]
```

```{r}
# 1. Load region shapefile (convert to sf for use with dplyr/ggplot2)
adm2_shp <- vect("data/data_raw/gadm/gadm41_BEN_2.shp")
adm2_sf <- st_as_sf(adm2_shp)
adm2_sf <- st_make_valid(adm2_sf)

df <- readRDS("data/data_rds/data_final.rds")

df_round5 <- df %>% filter(round == 5)
df_round8 <- df %>% filter(round == 8)

# Get the unique region identifiers in both rounds (intersection)
common_regions <- intersect(df_round5$NAME_2, df_round8$NAME_2)

# Filter original data to keep only the regions that appear in both rounds
df_common <- df %>% filter(iso=="BEN", NAME_2 %in% common_regions) %>% select(-NAME_2)

df_common%<>%filter(round==5)

# Convert to sf object (if not already)
df_sf <- st_as_sf(df_common, coords = c("longitude", "latitude"), crs = st_crs(adm2_sf))

# Proceed with spatial join or further analysis
df_adm2_sf <- st_join(df_sf, adm2_sf)

# 5. Aggregate: calculate mean trust by region
trust_mean <- df_adm2_sf %>%
  group_by(NAME_2, round) %>%  # replace with actual region ID column
  summarise(mean_trust = mean(trust_parl_a, na.rm = TRUE))

trust_mean_df <- st_drop_geometry(trust_mean)

# 6. Join aggregated data back to region geometries
regions_map <- adm2_sf %>%
  left_join(trust_mean_df, by = "NAME_2")  # make sure column name matches

capitals <- df_common %>%
  distinct(caplong, caplat, iso)%>%
  na.omit() %>%
  rename(longitude = caplong, latitude = caplat)

# 7. Plot the map
ggplot(regions_map) +
  geom_sf(aes(fill = mean_trust), color = "white") +
  scale_fill_gradient(
    low = "red",   # Low values will be red
    high = "green", # High values will be green
    na.value = "lightgrey",  # Missing values will be light grey
    limits = c(0, 3)  # Fix scale between 0 and 3

  ) +
  theme_minimal() +
  labs(
    title = "Trust - Round 5",
    fill = "Trust"
  )+
   geom_point(data = capitals, 
             aes(x = longitude, y = latitude), 
             size = 2, shape = 22, fill = "black", show.legend = FALSE)

# 1. Load region shapefile (convert to sf for use with dplyr/ggplot2)
adm2_shp <- vect("data/data_raw/gadm/gadm41_BEN_2.shp")
adm2_sf <- st_as_sf(adm2_shp)
adm2_sf <- st_make_valid(adm2_sf)

df <- readRDS("data/data_rds/data_final.rds")

df_round5 <- df %>% filter(round == 5)
df_round8 <- df %>% filter(round == 8)

# Get the unique region identifiers in both rounds (intersection)
common_regions <- intersect(df_round5$NAME_2, df_round8$NAME_2)

# Filter original data to keep only the regions that appear in both rounds
df_common <- df %>% filter(iso=="BEN", NAME_2 %in% common_regions) %>% select(-NAME_2)

df_common%<>%filter(round==8)

# Convert to sf object (if not already)
df_sf <- st_as_sf(df_common, coords = c("longitude", "latitude"), crs = st_crs(adm2_sf))

# Proceed with spatial join or further analysis
df_adm2_sf <- st_join(df_sf, adm2_sf)

# 5. Aggregate: calculate mean trust by region
trust_mean <- df_adm2_sf %>%
  group_by(NAME_2, round) %>%  # replace with actual region ID column
  summarise(mean_trust = mean(trust_parl_a, na.rm = TRUE))

trust_mean_df <- st_drop_geometry(trust_mean)

# 6. Join aggregated data back to region geometries
regions_map <- adm2_sf %>%
  left_join(trust_mean_df, by = "NAME_2")  # make sure column name matches

capitals <- df_common %>%
  distinct(caplong, caplat, iso)%>%
  na.omit() %>%
  rename(longitude = caplong, latitude = caplat)

# 7. Plot the map
ggplot(regions_map) +
  geom_sf(aes(fill = mean_trust), color = "white") +
  scale_fill_gradient(
    low = "red",   # Low values will be red
    high = "green", # High values will be green
    na.value = "lightgrey",  # Missing values will be light grey
    limits = c(0, 3)  # Fix scale between 0 and 3

  ) +
  theme_minimal() +
  labs(
    title = "Trust - Round 8",
    fill = "Trust"
  )+
   geom_point(data = capitals, 
             aes(x = longitude, y = latitude), 
             size = 2, shape = 22, fill = "black", show.legend = FALSE)

# 1. Load region shapefile (convert to sf for use with dplyr/ggplot2)
adm2_shp <- vect("data/data_raw/gadm/gadm41_BEN_2.shp")
adm2_sf <- st_as_sf(adm2_shp)
adm2_sf <- st_make_valid(adm2_sf)

df <- readRDS("data/data_rds/data_final.rds")

df_round5 <- df %>% filter(round == 5)
df_round8 <- df %>% filter(round == 8)

# Get the unique region identifiers in both rounds (intersection)
common_regions <- intersect(df_round5$NAME_2, df_round8$NAME_2)

# Filter original data to keep only the regions that appear in both rounds
df_common <- df %>% filter(iso=="BEN", NAME_2 %in% common_regions)

# 3. Aggregate: calculate mean trust by region and round (for both rounds 5 and 8)
trust_mean_by_round <- df_common %>%
  group_by(NAME_2, round) %>%
  summarise(mean_trust = mean(trust_parl_a, na.rm = TRUE), .groups = "drop")

# 4. Spread data: Create a wide format to compare rounds 5 and 8
trust_mean_wide <- trust_mean_by_round %>%
  pivot_wider(names_from = round, values_from = mean_trust) %>%
  rename(mean_trust_5 = `5`, mean_trust_8 = `8`)

# 5. Calculate the variation in trust (difference between round 8 and round 5)
trust_mean_wide <- trust_mean_wide %>%
  mutate(variation = mean_trust_8 - mean_trust_5)

# 6. Join the aggregated data back to the region geometries
regions_map <- adm2_sf %>%
  left_join(trust_mean_wide, by = "NAME_2")

# 7. Plot the variation map
ggplot(regions_map) +
  geom_sf(aes(fill = variation), color = "white") +
  scale_fill_gradient(
    low = "red",   # Low values will be red (indicating decrease in trust)
    high = "green", # High values will be green (indicating increase in trust)
    na.value = "lightgrey",  # Missing values will be light grey
    limits = c(-3, 3)  # Fix scale between -3 and 3 for variation
  ) +
  theme_minimal() +
  labs(
    title = "Trust (Round 8 - Round 5)",
    fill = "Delta"
  ) +
   geom_point(data = capitals, 
             aes(x = longitude, y = latitude), 
             size = 2, shape = 22, fill = "black", show.legend = FALSE)

```{r}
library(terra)
library(dplyr)
library(magrittr)
library(ggplot2)
library(tidyr)
library(gt)
library(rnaturalearth)

# Load survey data
df <- readRDS("data/data_rds/data_final.rds")

df%<>%
  filter(spl==1)

# Unique ISO codes in data
country_codes <- unique(df$iso)

# Path to admin2 shapefiles
shapefile_path <- "data/data_raw/gadm/"

# Store each country’s region vector
all_regions_vect <- list()

for (iso in country_codes) {
  shp_file <- paste0(shapefile_path, "gadm41_", iso, "_2.shp")

  if (!file.exists(shp_file)) {
    message("⛔ Skipping ", iso, " - shapefile missing.")
    next
  }

  message("✅ Processing ", iso)

  # Load shapefile
  adm2_vect <- vect(shp_file)

  # Filter country data and only include rounds 5 and 8
  df_country <- df %>% filter(iso == iso, round %in% c(5, 8))

  if (nrow(df_country) == 0) {
    message("⚠️ No data for rounds 5 or 8 for ", iso)
    adm2_vect$variation <- NA
    all_regions_vect[[iso]] <- adm2_vect
    next
  }

  df5 <- df_country %>% filter(round == 5)
  df8 <- df_country %>% filter(round == 8)
  common_regions <- intersect(df5$NAME_2, df8$NAME_2)

  if (length(common_regions) == 0) {
    message("⚠️ No common regions for ", iso)
    adm2_vect$variation <- NA
    all_regions_vect[[iso]] <- adm2_vect
    next
  }

  df_common <- df_country %>% filter(NAME_2 %in% common_regions)

  # Aggregate and calculate mean trust values
  trust_wide <- df_common %>%
    group_by(NAME_2, round) %>%
    summarise(trust = mean(trust_parl_a, na.rm = TRUE), .groups = "drop") %>%
    pivot_wider(names_from = round, values_from = trust, names_prefix = "R") %>%
    mutate(variation = R8 - R5)

  # Merge trust data back with spatial data
  adm2_vect$NAME_2 <- as.character(adm2_vect$NAME_2)
  joined <- tryCatch({
    merge(adm2_vect, trust_wide, by = "NAME_2", all.x = TRUE)
  }, error = function(e) {
    message("❌ Merge failed for ", iso, ": ", e$message)
    NULL
  })

  all_regions_vect[[iso]] <- joined
}

combined <- Reduce(rbind, all_regions_vect)
combined_df <- as.data.frame(combined)

capitals <- df %>%
  filter(round %in% c(5, 8)) %>%
  distinct(caplong, caplat, iso) %>%
  na.omit() %>%
  rename(longitude = caplong, latitude = caplat)

africa_outline <- ne_countries(continent = "Africa", returnclass = "sf") %>%
  st_make_valid()

africa_sf <- st_as_sf(combined)

ggplot() +
  geom_sf(data = africa_sf, aes(fill = variation), color = "white", linewidth = 0.1) +
  geom_sf(data = africa_outline, fill = NA, color = "black", linewidth = 0.2) +
  geom_point(data = capitals, aes(x = longitude, y = latitude),
             shape = 21, size = 2, fill = "black") +
  scale_fill_gradient2(
    low = "red", mid = "white", high = "green",
    midpoint = 0, limits = c(-3, 3),
    na.value = "lightgrey",
    name = "Δ Trust\n(R8 - R5)"
  ) +
  theme_minimal() +
  labs(
    title = "Trust Change in Parliament (Round 8 - Round 5)",
    subtitle = "Across African Regions",
    caption = "Grey = No data"
  )
```

```{r}
# Define which countries use which admin level
countries_adm1 <- c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")
countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE")

# Load required libraries
library(magrittr)
library(dplyr)
library(tidyr)
library(terra)
library(sf) # For better spatial data handling

# Load data
df <- readRDS("data/data_rds/data_final.rds")
df %<>% filter(spl == 1)

# Unique ISO codes in data
country_codes <- unique(df$iso)

# Path to admin shapefiles
shapefile_path <- "data/data_raw/gadm/"

# Store each country's region vector - keeping as sf objects until the end
all_regions_sf <- list()

for (iso_code in country_codes) {
  # Skip if not in our specified lists
  if (!(iso_code %in% c(countries_adm1, countries_adm2))) {
    message("⛔ Skipping ", iso_code, " - not in specified admin level lists.")
    next
  }

  # Determine admin level for this country
  admin_level <- if(iso_code %in% countries_adm1) 1 else 2

  # Build shapefile path based on admin level
  shp_file <- paste0(shapefile_path, "gadm41_", iso_code, "_", admin_level, ".shp")

  if (!file.exists(shp_file)) {
    message("⛔ Skipping ", iso_code, " - shapefile missing at admin level ", admin_level)
    next
  }

  message("✅ Processing ", iso_code, " at admin level ", admin_level)

  # Load shapefile with sf for more reliable handling
  adm_sf <- sf::st_read(shp_file, quiet = TRUE)

  # Get the appropriate region name field based on admin level
  region_field <- paste0("NAME_", admin_level)

  # Make sure the field exists in the shapefile
  if(!(region_field %in% names(adm_sf))) {
    message("⚠️ Field ", region_field, " not found in shapefile for ", iso_code)
    next
  }

  # Filter country data and only include rounds 5 and 8
  df_country <- df %>% filter(iso == iso_code, round %in% c(5, 8))

  if (nrow(df_country) == 0) {
    message("⚠️ No data for rounds 5 or 8 for ", iso_code)
    adm_sf$variation <- NA_real_
    all_regions_sf[[iso_code]] <- adm_sf
    next
  }

  # Ensure we're using the correct region field in the data
  # Check if fields exist in df_country
  if(!(region_field %in% names(df_country))) {
    message("⚠️ Field ", region_field, " not found in data for ", iso_code)
    adm_sf$variation <- NA_real_
    all_regions_sf[[iso_code]] <- adm_sf
    next
  }

  # Split by round
  df5 <- df_country %>% filter(round == 5)
  df8 <- df_country %>% filter(round == 8)

  # Find common regions between rounds
  common_regions <- intersect(df5[[region_field]], df8[[region_field]])

  if (length(common_regions) == 0) {
    message("⚠️ No common regions for ", iso_code)
    adm_sf$variation <- NA_real_
    all_regions_sf[[iso_code]] <- adm_sf
    next
  }

  # Filter to common regions
  df_common <- df_country %>% filter(!!sym(region_field) %in% common_regions)

  # Debug: Print a sample of region names to verify structure
  message("Sample regions for ", iso_code, ": ", 
          paste(head(unique(df_common[[region_field]]), 3), collapse=", "))

  # Aggregate and calculate mean trust values
  trust_wide <- df_common %>%
    group_by(!!sym(region_field), round) %>%
    summarise(trust = mean(trust_parl_a, na.rm = TRUE), .groups = "drop") %>%
    pivot_wider(names_from = round, values_from = trust, names_prefix = "R") %>%
    mutate(variation = R8 - R5)

  # Debug: Check trust_wide structure
  message("Trust data structure: ", nrow(trust_wide), " rows with variation calculated")

  # Convert region names to character for reliable joining
  adm_sf[[region_field]] <- as.character(adm_sf[[region_field]])
  trust_wide[[region_field]] <- as.character(trust_wide[[region_field]])

  # Left join instead of merge for more reliable behavior
  joined <- tryCatch({
    sf::st_join(adm_sf, trust_wide, by = region_field, join = st_equals)
  }, error = function(e) {
    # Try a different join method if st_equals fails
    tryCatch({
      left_join(adm_sf, trust_wide, by = region_field)
    }, error = function(e2) {
      message("❌ Join failed for ", iso_code, ": ", e2$message)
      message("SHP fields: ", paste(head(names(adm_sf)), collapse=", "))
      message("Data fields: ", paste(head(names(trust_wide)), collapse=", "))
      NULL
    })
  })

  if(!is.null(joined)) {
    all_regions_sf[[iso_code]] <- joined
    # Debug: Check for NAs in variation
    na_count <- sum(is.na(joined$variation))
    total_count <- nrow(joined)
    message("Variation has ", na_count, " NAs out of ", total_count, " regions")
  }
}

# Only combine non-NULL elements
valid_regions <- all_regions_sf[!sapply(all_regions_sf, is.null)]

if(length(valid_regions) > 0) {
  # Check if we can rbind these objects
  if(length(valid_regions) > 1) {
    # Make sure all objects have compatible columns
    all_cols <- unique(unlist(lapply(valid_regions, names)))
    for(i in seq_along(valid_regions)) {
      missing_cols <- setdiff(all_cols, names(valid_regions[[i]]))
      for(col in missing_cols) {
        valid_regions[[i]][[col]] <- NA
      }
    }
  }

  # Now bind them safely
  combined <- do.call(rbind, valid_regions)

  # Convert back to terra format if needed
  combined_vect <- terra::vect(combined)
  combined_df <- as.data.frame(combined_vect)

  # Save or continue processing
} else {
  message("No valid data to combine")
}

capitals <- df %>%
  filter(round %in% c(5, 8)) %>%
  distinct(caplong, caplat, iso) %>%
  na.omit() %>%
  rename(longitude = caplong, latitude = caplat)

africa_outline <- ne_countries(continent = "Africa", returnclass = "sf") %>%
  st_make_valid()

africa_sf <- st_as_sf(combined)

ggplot() +
  geom_sf(data = africa_sf, aes(fill = variation), color = "white", linewidth = 0.1) +
  geom_sf(data = africa_outline, fill = NA, color = "black", linewidth = 0.2) +
  geom_point(data = capitals, aes(x = longitude, y = latitude),
             shape = 21, size = 2, fill = "black") +
  scale_fill_gradient2(
    low = "red", mid = "white", high = "green",
    midpoint = 0, limits = c(-3, 3),
    na.value = "lightgrey",
    name = "Δ Trust\n(R8 - R5)"
  ) +
  theme_minimal() +
  labs(
    title = "Trust Change in Parliament (Round 8 - Round 5)",
    subtitle = "Across African Regions",
    caption = "Grey = No data"
  )
```

```{r}
# Define which countries use which admin level
countries_adm1 <- c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")
countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE")

# Load required libraries
library(magrittr)
library(dplyr)
library(tidyr)
library(terra)
library(sf)

# Load data
df <- readRDS("data/data_rds/data_final.rds")
df %<>% filter(spl == 1)

# Unique ISO codes in data
country_codes <- unique(df$iso)

# Path to admin shapefiles
shapefile_path <- "data/data_raw/gadm/"

# Store each country's region vector
all_regions_sf <- list()

for (iso_code in country_codes) {
  # Skip if not in our specified lists
  if (!(iso_code %in% c(countries_adm1, countries_adm2))) {
    message("⛔ Skipping ", iso_code, " - not in specified admin level lists.")
    next
  }

  # Determine admin level for this country
  admin_level <- if(iso_code %in% countries_adm1) 1 else 2

  # Build shapefile path based on admin level
  shp_file <- paste0(shapefile_path, "gadm41_", iso_code, "_", admin_level, ".shp")

  if (!file.exists(shp_file)) {
    message("⛔ Skipping ", iso_code, " - shapefile missing at admin level ", admin_level)
    next
  }

  message("✅ Processing ", iso_code, " at admin level ", admin_level)

  # Load shapefile with sf
  adm_sf <- sf::st_read(shp_file, quiet = TRUE)

  # Get the appropriate region name field based on admin level
  region_field <- paste0("NAME_", admin_level)

  # Make sure the field exists in the shapefile
  if(!(region_field %in% names(adm_sf))) {
    message("⚠️ Field ", region_field, " not found in shapefile for ", iso_code)
    next
  }

  # Filter country data to include rounds 5-8
  df_country <- df %>% filter(iso == iso_code, round >= 5, round <= 8)

  if (nrow(df_country) == 0) {
    message("⚠️ No data for rounds 5-8 for ", iso_code)
    adm_sf$variation <- NA_real_
    adm_sf$min_round <- NA_integer_
    adm_sf$max_round <- NA_integer_
    all_regions_sf[[iso_code]] <- adm_sf
    next
  }

  # Ensure we're using the correct region field in the data
  if(!(region_field %in% names(df_country))) {
    message("⚠️ Field ", region_field, " not found in data for ", iso_code)
    adm_sf$variation <- NA_real_
    adm_sf$min_round <- NA_integer_
    adm_sf$max_round <- NA_integer_
    all_regions_sf[[iso_code]] <- adm_sf
    next
  }

  # Calculate average trust by region and round
  region_trust <- df_country %>%
    group_by(!!sym(region_field), round) %>%
    summarise(trust = mean(trust_parl_a, na.rm = TRUE), .groups = "drop")

  # Find regions with at least 2 rounds of data
  region_round_counts <- region_trust %>%
    group_by(!!sym(region_field)) %>%
    summarise(num_rounds = n(), .groups = "drop")

  regions_with_multiple_rounds <- region_round_counts %>%
    filter(num_rounds >= 2) %>%
    pull(!!sym(region_field))

  if (length(regions_with_multiple_rounds) == 0) {
    message("⚠️ No regions with multiple rounds for ", iso_code)
    adm_sf$variation <- NA_real_
    adm_sf$min_round <- NA_integer_
    adm_sf$max_round <- NA_integer_
    all_regions_sf[[iso_code]] <- adm_sf
    next
  }

  # Filter to regions with multiple rounds
  region_trust_filtered <- region_trust %>%
    filter(!!sym(region_field) %in% regions_with_multiple_rounds)

  # For each region, calculate variation between earliest and latest available round
  variation_data <- region_trust_filtered %>%
    group_by(!!sym(region_field)) %>%
    summarise(
      min_round = min(round),
      max_round = max(round),
      earliest_trust = trust[which.min(round)],
      latest_trust = trust[which.max(round)],
      variation = latest_trust - earliest_trust,
      .groups = "drop"
    )

  # Debug info
  message("Found ", nrow(variation_data), " regions with variations for ", iso_code)

  # Convert region names to character for reliable joining
  adm_sf[[region_field]] <- as.character(adm_sf[[region_field]])
  variation_data[[region_field]] <- as.character(variation_data[[region_field]])

  # Join variation data with shapefile
  joined <- left_join(adm_sf, variation_data, by = region_field)

  if(!is.null(joined)) {
    all_regions_sf[[iso_code]] <- joined
    # Debug: Check for NAs in variation
    na_count <- sum(is.na(joined$variation))
    total_count <- nrow(joined)
    message("Variation has ", na_count, " NAs out of ", total_count, " regions")
  }
}

# Only combine non-NULL elements
valid_regions <- all_regions_sf[!sapply(all_regions_sf, is.null)]

if(length(valid_regions) > 0) {
  # Ensure column compatibility
  all_cols <- unique(unlist(lapply(valid_regions, names)))
  for(i in seq_along(valid_regions)) {
    missing_cols <- setdiff(all_cols, names(valid_regions[[i]]))
    for(col in missing_cols) {
      valid_regions[[i]][[col]] <- NA
    }
  }

  # Combine all regions
  combined <- do.call(rbind, valid_regions)

  # Convert back to terra format if needed
  combined_vect <- terra::vect(st_cast(combined))
  combined_df <- as.data.frame(combined_vect)

  # Summary of variations
  message("Variation summary:")
  message("Min: ", min(combined$variation, na.rm = TRUE))
  message("Max: ", max(combined$variation, na.rm = TRUE))
  message("Mean: ", mean(combined$variation, na.rm = TRUE))
  message("Median: ", median(combined$variation, na.rm = TRUE))
  message("NA count: ", sum(is.na(combined$variation)))

  # You can now proceed with further analysis or visualization
} else {
  message("No valid data to combine")
}

capitals <- df %>%
  filter(round %in% c(5, 8)) %>%
  distinct(caplong, caplat, iso) %>%
  na.omit() %>%
  rename(longitude = caplong, latitude = caplat)

africa_outline <- ne_countries(continent = "Africa", returnclass = "sf") %>%
  st_make_valid()

africa_outline <- st_transform(africa_outline, st_crs(combined))

africa_sf <- st_as_sf(combined)

ggplot() +
  geom_sf(data = africa_sf, aes(fill = variation), color = "white", linewidth = 0.1) +
  geom_sf(data = africa_outline, fill = NA, color = "black", linewidth = 0.2) +
    geom_point(data = capitals, aes(x = longitude, y = latitude),
             shape = 21, size = 2, fill = "black") +
  scale_fill_gradient2(
    low = "red", high = "green",
    midpoint = 0, limits = c(-2, 2),
    na.value = "lightgrey",
    name = "Δ Trust\n(R8 - R5)"
  ) +
  theme_minimal() +
  labs(
    title = "Trust Change in Parliament (Round 8 - Round 5)",
    subtitle = "Across African Regions",
    caption = "Grey = No data"
  )
```
